External Patch Group Prior Guided Internal Subspace Learning for Real Image Denoising

### 2016-10-11 egpaper_for_review.tex
a

\subsection{The Overall Algorithm}
%------------------------------------------------------------------------
\section{Experiments}
In this section, we perform real image image denoising experiments on three standard datasets. The first dataset is real noisy images with mean images as ground truths. The second dataset is provided by the website of Noise Clinic. The third dataset is provided by the Commercial software Neat Image. The second and third dataset do not have ground truth images.

\subsection{Parameters Setting}
The proposed method contains the PG prior learning stage, the external prior guided internal subspace learning stage, and the denoising stage. In the learning stage, similar to the PGPD, there are four parameters, $p$, $M$, $W$, and $K$.  We set $p=6$ and hence the patch size is $6\times 6 \times 3$. The winodw size for searching PGs is W = 31. The number of similar patches is $N=10$, the number of cluters is set as $K = 33$. In the external prior guided learning stage, there is no parameters. In the denoising stage, there are one paramters, i.e., the $\lambda$ which is used to regularize the sparse term.

@@

\subsection{Real Image Denoising}
We evaluate the competing denoising methods from various research directions on two datasets. Both the two datasets comes from the \cite{crosschannel2016}. The first contains 3 cropped images of size $512\times512$. The other dataset contains 42 images cropped to size of $500\times500$ from the 17 images provided in \cite{crosschannel2016}. The 60 images contain most of the scenes in the 17 images \cite{crosschannel2016}.
\begin{table*}
\caption{Average PSNR(dB) results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
1& 37.00 & 37.08 & 37.09 &  37.46  &  37.51  &  32.91  & \textbf{ 38.76}  & 37.68   & 38.63  
\\
\hline
2& 33.88 & 33.95  &  33.95  &  34.90  &  35.04  & 31.94   &  35.69  &  34.87  & \textbf{ 35.96 }
\\
\hline
3& 33.83  & 33.85  & 33.85   & 34.15   &   34.07 & 30.89   & \textbf{35.54 }  &  34.77  &  35.51 
\\
\hline
Average & 34.90  &  34.96 &  34.96  & 35.50   & 35.54   &  31.91  &  36.67  &  35.77  &  \textbf{ 36.70}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\caption{Average SSIM results of different methods on 3 real noisy images captured by Canon EOS 5D mark3 at ISO3200 in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
1& 0.9345 & 0.9368  & 0.9372  & 0.9599   &  0.9607  & 0.9043   &  0.9689  & 0.9600   &\textbf{ 0.9712  }
\\
\hline
2& 0.8919 &  0.8848 &  0.8951 & 0.9159   &  0.9187  &  0.8498  &  0.9427  &  0.9308  & \textbf{ 0.9434 }
\\
\hline
3& 0.9128  & 0.9136 & 0.9136  & 0.9254   &  0.9279  &  0.8635  &  0.9476  & 0.9463   & \textbf{ 0.9529 }
\\
\hline
Average &  0.9131  & 0.9117 &  0.9153 & 0.9337   & 0.9358   &  0.8725  & 0.9531   & 0.9457   &  \textbf{0.9558} 
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}
\caption{Average PSNR(dB) and SSIM results of different methods on 42 cropped images from 17 real noisy images in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|}
\hline
Measure & \textbf{Noisy} &\textbf{BM3D}&\textbf{WNNM}&\textbf{CSF}&\textbf{TRD}&\textbf{MLP}& \textbf{Noise Clinic}& \textbf{Neat Image}&\textbf{Ours}
\\
\hline
PSNR& 34.36 & 34.36 & 34.40 & 36.11 & 36.05 & 34.41 & 37.68 & 36.58 & 36.15
\\
\hline
SSIM& 0.8552 & 0.8553 & 0.8577 & 0.9215 & 0.9211 & 0.9012 & 0.9470 & 0.9145 & 0.9236
\\
\hline
\end{tabular}
\end{center}
\end{table*}

>>>>

\subsection{The Overall Algorithm}
%------------------------------------------------------------------------
\section{Experiments}
In this section, we perform real image image denoising experiments on three standard datasets. The first dataset is real noisy images with mean images as ground truths provided by \cite{crosschannel2016}. The second dataset is provided by the website of Noise Clinic \cite{noiseclinic}. The third dataset is provided by the Commercial software Neat Image \cite{neatimage}. The second and third dataset do not have ground truth images.

\subsection{Parameters Setting}
The proposed method contains the PG prior learning stage, the external prior guided internal subspace learning stage, and the denoising stage. In the learning stage, similar to the PGPD, there are four parameters, $p$, $M$, $W$, and $K$.  We set $p=6$ and hence the patch size is $6\times 6 \times 3$. The winodw size for searching PGs is $W = 31$. The number of similar patches is $N=10$, the number of cluters is set as $K = 33$. In the external prior guided learning stage, there is no parameters. In the denoising stage, there are one paramters, i.e., the $\lambda$ which is used to regularize the sparse term.

@@

\subsection{Real Image Denoising}
We  the competing denoising methods from various research directions on two datasets. Both the two datasets comes from the \cite{crosschannel2016}. The first dataset contains 17 images of size over $7000\times5000$. Since this dataset contains recurrent contents across different images, we crop 60 small images of size $500\times500$ from these 17 images in \cite{crosschannel2016}.

The PSNR and SSIM resluts are listed in table \ref{tab1}.
\begin{table*}\label{tab1}
\caption{Average PSNR(dB) results of different methods on 60 cropped real noisy images captured in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 34.51  &  34.58 &  34.52  & 36.19   & 37.40 &  36.53  &  37.57  & 37.66 & 37.92 &  \textbf{ 38.46}
\\
\hline
SSIM & 0.8718  & 0.8748  & 0.8743   & 0.9470 & 0.9598  & 0.9241  &  0.9514  & 0.9495  & 0.9625 &   \textbf{0.9677}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

\begin{table*}\label{tab2}
\caption{Average PSNR(dB) results of different methods on 15 cropped real noisy images used in \cite{crosschannel2016}.}
\label{tab1}
\begin{center}
\renewcommand\arraystretch{1}
\begin{tabular}{|c||c|c|c|c|c|c|c|c|c|c|c|c|}
\hline
Image & \textbf{Noisy} &\textbf{CBM3D}&\textbf{WNNM}&\textbf{MLP}&\textbf{CSF}& \textbf{NI}& \textbf{NC}& \textbf{CC}&\textbf{Offline} &\textbf{Online} &\textbf{Guided} 
\\
\hline
PSNR & 33.41  &  33.48 &  33.48  & 36.49   & 35.33 &  35.49   &  36.43  &  36.88  & 36.69 & 36.75 &  \textbf{ 37.04}
\\
\hline
SSIM & 0.8483  & 0.8511  & 0.8512   & 0.9444 & 0.9250  & 0.9126  &  0.9364  & 0.9481  & 0.9486 & 0.9485 &  \textbf{ 0.9509}
\\
\hline
\end{tabular}
\end{center}
\end{table*}

%\\
%\hline
%1 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 40.13 }
%\\
%\hline
%2 &    &    &     &     &    &      &     &     &   & 37.09  &  \textbf{ 36.99 }
%\\
%\hline
%3 &    &    &     &     &    &      &     &     &   & 36.58  &  \textbf{ 36.92 }
%\\
%\hline
%4 &    &    &     &     &    &      &     &     &   & 34.85  &  \textbf{ 35.11 }
%\\
%\hline
%5 &    &    &     &     &    &      &     &     &   &  36.12 &  \textbf{ 36.50 }
%\\
%\hline
%6 &    &    &     &     &    &      &     &     &   & 38.92  &  \textbf{ 38.74 }
%\\
%\hline
%7 &    &    &     &     &    &      &     &     &   & 38.30  &  \textbf{ 38.30 }
%\\
%\hline
%8 &    &    &     &     &    &      &     &     &   &  39.48 &  \textbf{ 40.26 }
%\\
%\hline
%9 &    &    &     &     &    &      &     &     &   & 38.72  &  \textbf{ 38.68 }
%\\
%\hline
%10 &    &    &     &     &    &      &     &     &   & 38.38  &  \textbf{ 38.35 }
%\\
%\hline
%11 &    &    &     &     &    &      &     &     &   & 36.42  &  \textbf{ 36.77 }
%\\
%\hline
%12 &    &    &     &     &    &      &     &     &   & 38.35  &  \textbf{ 38.41 }
%\\
%\hline
%13 &    &    &     &     &    &      &     &     &   & 33.26  &  \textbf{ 33.61 }
%\\
%\hline
%14 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.40 }
%\\
%\hline
%15 &    &    &     &     &    &      &     &     &   &   &  \textbf{ 33.47 }
